NumPy---Array Programming in Python

### 2020-01-25 body.tex
Minor edits

NumPy has subsequently seen prolific adoption, with millions of users,
first from research and later also industry.
It spurred the development of the larger scientific Python ecosystem and
heralded the current era of wide-spread use of Python for scientific computing.
The reasons for its success are complex, but include the fact NumPy
(a) is built on top of Python, (b) has a strong culture of collaboration
and good software development practices, and (c) provides one of the
best array programming environments for scientific data analysis.

\emph{Python} is an open source, general-purpose, interpreted programming language
well-suited to standard programming tasks such as cleaning data,
interacting with web resources, and parsing text.
Adding fast array operations and linear algebra allows scientist to do all
their work within a single language---and one that has the advantage of
being famously easy to learn and teach.
In fact, Python's adoption as
a primary learning language in many universities (e.g., many lower division
UC Berkeley courses use Python including Foundations of Data Science,
The Beauty and Joy of Computing,
Introduction to Computational Thinking with Data,
and The Structure and Interpretation of Computer Programs) has
further popularized NumPy as a tool of choice for modern data science.

Even though NumPy is not part of Python's standard library,
we have a health relationship to the core development team.
\fixme{we've gotten a number of features: slicing syntax, implicit tuples,
complex numbers, buffer protocol, matrix multiplication operator}
\fixme{but we benefit from separate governance}

@@

NumPy combines the performance of C, the expressive power of array
programming, and the Python programming language in a mature
well-tested and well-documented community developed library.
It builds on decades of work refining the array programming
syntax from APL through Yorick and others.
It also made it easy for other libraries to develop fast and
memory-efficient compiled code, usually in C or Fortran, that could manipulate
these arrays and pass them back to Python.
Popular libraries increased the user community and that
in turn led to new libraries adding additional functionality
to the scientific Python ecosystem in a virtuous cycle.

>>>>

NumPy has subsequently seen prolific adoption, with millions of users,
first from research and later also industry.
It spurred the development of the larger scientific Python ecosystem and
heralded the current era of wide-spread use of Python for scientific computing.
The reasons for its success are complex, but include the fact that
NumPy (a) is built on top of Python,
(b) has a strong culture of collaboration and good software development practices, and
(c) provides a cutting-edge array programming environment for scientific data analysis.

\emph{Python} is an open source, general-purpose, interpreted programming language
well-suited to standard programming tasks such as cleaning data,
interacting with web resources, and parsing text.
Adding fast array operations and linear algebra allows scientist to do all
their work within a single language---and one that has the advantage of
being famously easy to learn and teach.
In fact, Python's adoption as a primary learning language in universities
(e.g., many lower division UC Berkeley courses use Python including
Foundations of Data Science,
The Beauty and Joy of Computing,
Introduction to Computational Thinking with Data,
and The Structure and Interpretation of Computer Programs) has
further popularized NumPy as a tool of choice for modern data science.

Even though NumPy is not part of Python's standard library,
we benefit from a good relationship with the Python developers.
Over the years, the Python language has added new features and
special syntax so that NumPy would have more succinct and 
easy to read array notation.
Since we are not part of the standard library, we are able to
dictate our own release policies and development patterns.
%\fixme{we've gotten a number of features: slicing syntax, implicit tuples,
%complex numbers, buffer protocol, matrix multiplication operator}
%\fixme{but we benefit from separate governance}

@@

NumPy combines the performance of C, the expressive power of array
programming, and the Python programming language in a mature
well-tested and well-documented community developed library.
It builds on decades of work refining the array programming
syntax from APL through Yorick and others.
It also made it easy for other libraries to develop fast and
memory-efficient compiled code, usually in C or Fortran, that could manipulate
these arrays and pass them back to Python.
Popular array-aware libraries increased the user community and that
in turn led to more libraries adding new functionality
to the scientific Python ecosystem.

### 2020-01-25 methods.tex
Minor edits

Finally, since May 2019 the project receives around 10K USD annually from
Tidelift, a part of which is used to fund documentation and website
improvements.

@@

Finally, a \code{SeedSequence} is used to initialize a bit generator. The seed
sequence can be initialized with no arguments, in which case it reads entropy
from a system-dependent provider, or with a user-provided seed. The seed
sequence then transforms the initial set of entropy into a sequence of
high-quality pseudorandom integers, which can be used to initialize multiple bit
generators deterministically. The key feature of a seed sequence is that
it can be used to spawn child \code{SeedSequence}s which allow to initialize
multiple distinct bit generators.
% Of course there is a diminishing chance of collisions...
% Only found http://www.pcg-random.org/posts/developing-a-seed_seq-alternative.html
% as a reference for seed sequence, it would be nice to cite something.
This capability allows a seed sequence to facilitate large distributed applications
where the number of workers required is not known. The sequences generated from
the same initial entropy and spawns are fully deterministic to ensure
reproducibility.

>>>>

Finally, since May 2019 the project receives a small amount annually from
Tidelift, which is used to fund things like documentation and website
improvements.

@@

Finally, a \code{SeedSequence} is used to initialize a bit generator. The seed
sequence can be initialized with no arguments, in which case it reads entropy
from a system-dependent provider, or with a user-provided seed. The seed
sequence then transforms the initial set of entropy into a sequence of
high-quality pseudorandom integers, which can be used to initialize multiple bit
generators deterministically. The key feature of a seed sequence is that
it can be used to spawn child \code{SeedSequence}s to initialize
multiple distinct bit generators.
% Of course there is a diminishing chance of collisions...
% Only found http://www.pcg-random.org/posts/developing-a-seed_seq-alternative.html
% as a reference for seed sequence, it would be nice to cite something.
This capability allows a seed sequence to facilitate large distributed applications
where the number of workers required is not known. The sequences generated from
the same initial entropy and spawns are fully deterministic to ensure
reproducibility.
